Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/paper.tex
Refraction Networking

In this paper, we present \textbf{\scheme}, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements~\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

\subsection{Registration}
\label{sec:registration}
We use a form of refraction networking similar to Tapdance to register directly with
the station, though \scheme registration is significantly simpler and more difficult
to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
a client communicates their intent to register to the station without any 
response from the station itself. This makes registration flows very difficult to detect as they 
can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.

@@

Our \scheme client is written in Golang, and uses the refraction networking tagging
schema (Section~\ref{sec:registration}) for
registration. We note that this protocol will be more difficult for censors to observe
than normal TapDance because it consists of only a single (complete) request, and the station does
not have to spoof packets as the decoy during registration, only passively
observe them.

>>>>

In this paper, we present \textbf{\scheme}, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

\subsection{Registration}
\label{sec:registration}
We use a form of Refraction Networking similar to Tapdance to register directly with
the station, though \scheme registration is significantly simpler and more difficult
to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
a client communicates their intent to register to the station without any 
response from the station itself. This makes registration flows very difficult to detect as they 
can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.

@@

Our \scheme client is written in Golang, and uses the Refraction Networking tagging
schema (Section~\ref{sec:registration}) for
registration. We note that this protocol will be more difficult for censors to observe
than normal TapDance because it consists of only a single (complete) request, and the station does
not have to spoof packets as the decoy during registration, only passively
observe them.
